Draft

### 2017-06-29 Thesis/Draft.Rmd
Scripts for calibrating algorithms

The idea now is that we would like to classify the banners into two distinct groups: A group with a mean conversion rate $\mu_i$ below threshold $\tau$, and a group with mean conversion rate $\mu_i$ above threshold $\tau$. This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.

@@

In any case, the problem boils down to the following. As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed accoring to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. In the case of pure exploration bandits, it is for example necessary to compare the arms because one aims to find the best one. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow a $R$-sub-Gaussian distribution. Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound. Both hinge upon the *complexity* of a given problem. Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others. Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold. Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$. For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.

If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$. In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify. (WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM? WHAT IS ITs MOTIVATION? ITS NOT THAAAT NATURAL)

@@

Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize. As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret. The notion of regret considered in the thresholding bandit, however, is more akin to the regret in pure exploration bandits or the error probability in sequential hypothesis testing. Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm. Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$. Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$. At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$. We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$. Let $T$ be the overall number of samples the algorithm is allowed to pull. We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$. That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified. It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss. These arms are considered close enough to the threshold that we do not care whether they lie above or below.

@@

From the general setup, we already know how the algorithm will end. After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated until time $T$. Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$. For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including). Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.

@@

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision. Of course, that's just Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate.

@@

Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian. This is mentioned in Locatelli et al. (2016). In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta_i}(t)$ are motivated by (sub-)Gaussian distributions. The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however. In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions. Locatelli et al. (2016) thus refers to Bubeck et al. (2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions. By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.

Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al. (2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution. Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper. We will continue to discuss the Augmented UCB solution further in chapter 3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly. While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian. This, for example, is the case for Bernoulli distributions at very small parameters $\mu$. It's quite obvious simply by looking at examples that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation. The second graph then shows, that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values. Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.

@@

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (seq(0.00001,0.3, by = 0.000005)-i)^2)
}
par(mfcol = c(1,1))
```

@@

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1.5), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (i-seq(0.00001,0.3, by = 0.000005))^2)
}
par(mfcol = c(1,1))
```

@@

*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem 1 of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).

@@

#### Reminder about the goal of the proof

@@

#### Statistical Decision

@@

#### Change of Distribution

@@

#### Concentration of the Empirical Kullback-Leibler Divergence

@@

#### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$

@@

#### Bringing everything together

@@

The Hoeffding inequality as used here is as follows:

@@

#### Step 2: Lower Bound on Number of Pulls of Difficult Arm

@@

#### Step 3: Lower Bound on Number of Pulls of Simple Arm

@@

#### Conclusion

@@

Even though the complexity $H$ enjoys popularity in the literature of the best m arm identification problem, $m \geq 1$, Kaufmann et al. (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions. Indeed, they go so far as to define new measures of complexity that are based on information theoretic metrics. Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions. In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.

@@

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above. Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3. Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:

@@

To proof this statement, we assume as before that the arms are ordered by their means decreasing in size. For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions, there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$. In this alternative model, only arm $a$ is modified in accordance with the continuity conditions. Modified in such a way that measured by the Kullback-Leibler divergence, the arm $\nu_{m+1}$ is now closer to $\nu_a$ than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$). On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$). These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$ no longer optimal under the alternative model $\nu'$. Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the by the stopping time $\tau$ induced $\sigma$-Algebra $\mathcal{F}_{\tau}$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).

@@

\begin{theorem}[Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

@@

#### Matching algorithm strategies

Given those lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.

@@

A very similar application of the KL divergence has been given in Garivier and Kaufmann to derive a lower bound on the sample complexity in the case of best arm identification. In particular, the transportation Lemma 1 is used again. And a matching algorithm for $K \geq 2$ arms is proposed.

@@

>>>>

The idea now is that we would like to classify the banners into two distinct groups: A group with mean conversion rates $\mu_i$ below threshold $\tau$, and a group with mean conversion rates $\mu_i$ above threshold $\tau$. This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.

@@

In any case, the problem boils down to the following. As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution. Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound. Both hinge upon the *complexity* of a given problem. Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others. Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold. Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$. For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.

If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$. In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify. (WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?)

@@

Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize. As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret. The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing. Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm. Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$. Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$. At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$. We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$. Let $T$ be the overall number of samples the algorithm is allowed to pull. We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$. That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified. It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss. These arms are considered close enough to the threshold that we do not care whether they lie above or below.

@@

From the general setup, we already know how the algorithm will end. After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$. Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$. For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including). Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.

@@

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision. This is Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate. (?)

@@

Where the APT algorithm shows room for improvement is when it comes to settings with distributions that are not sub-Gaussian. This is mentioned in Locatelli et al. (2016). In general, the problem becomes that the assumptions for the bounds no longer hold; furthermore, the statistic $B_i(t+1)$, and the term $\hat{\Delta}_i(t)$ are motivated by (sub-)Gaussian distributions. The more one moves away from Gaussian-like distributions, the less appropriate this term becomes, however. In particular, the empirical mean will be less concentrated around the true mean and more impacted by outliers which are more likely under non sub-Gaussian distributions. Locatelli et al. (2016) thus refers to Bubeck et al. (2013) which considers solutions for multi-armed bandits that are based on heavy-tail distributions. By using more robust estimators of the mean, one could equip the APT algorithm to deal with such distributions.

Another step towards dealing with non sub-Gaussianity is made by Mukherjee et al. (2017) who use an estimate of the variance additionally to the empirical mean in their Augmented UCB solution. Utilizing this additional information, the algorithm seems to perform better than for example APT, going from simulation results displayed in the paper. However, the simulations deal exclusively with normal distributions, as the variance has to be bounded for the upper bound of the Augmented UCB to hold. We will continue to discuss the Augmented UCB solution in chapter 3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly. While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian. This, for example, is the case for Bernoulli distributions at very small parameters $\mu$. By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation. The second graph then shows that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values. Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.

@@

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (seq(0.00001,0.3, by = 0.000005)-i)^2)
}
par(mfcol = c(1,1))
```

@@

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (i-seq(0.00001,0.3, by = 0.000005))^2)
}
par(mfcol = c(1,1))
```

@@

*Proof of Theorem \ref{theorem:Locatelli2016Theorem1}*: In Theorem \ref{theorem:Locatelli2016Theorem1} of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).

@@

### Reminder about the goal of the proof

@@

### Statistical Decision

@@

### Change of Distribution

@@

### Concentration of the Empirical Kullback-Leibler Divergence

@@

### Bounding $T_i$ for $\max_{i \in \{1,\dots,K\}}\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$

@@

### Bringing everything together

@@

The Hoeffding inequality as used here is as follows (compare chapter 2.4 in [David Pollard (2015)](http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf)):

@@

### Step 2: Lower Bound on Number of Pulls of Difficult Arm

@@

### Step 3: Lower Bound on Number of Pulls of Simple Arm

@@

### Conclusion

@@

Even though the complexity $H$ enjoys popularity in the literature of the best $m$ arm identification problem, $m \geq 1$, Kaufmann et al. (2016) show explicitly that $H$ is mainly useful for problems of Gaussian distributions. Indeed, they go so far as to define new measures of complexity that are based on information theoretic measures Using those they then display $H$ as an approximation to their measures in the case of Gaussian distributions. In turn, this makes apparent that especially Bernoulli distributions with small means have to be treated differently.

@@

\begin{theorem}[Theorem 4, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem4}
Let $\nu \in \mathcal{M}_m$, where $\mathcal{M}_m$ is the set of uniquely identifiable bandit models described above. Assume that $\mathcal{P}$ satisfies the continuity conditions in Assumption 3. Any $\delta$-PAC algorithm on $\mathcal{M}_m$ satisfies, for $\delta \leq 0.15$:

@@

To proof this statement, we assume as before that the arms are ordered by their means decreasing in size. For a given $\delta$-PAC algorithm $\mathcal{A} = ((A_t), \tau, \hat{S}_m)$, and under the continuity conditions (compare Kaufmann et al. (2016)), there exists for every arm $a \in \{1, \dots, K\}$ an alternative model $\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)$. In this alternative model, only arm $a$ is modified in accordance with the continuity conditions. Modified in such a way that measured by the Kullback-Leibler divergence, the arm $\nu_{m+1}$ is now closer to $\nu_a$ than $\nu_a'$ is to $\nu_a$, if $\mu_a > \mu_{m+1}$ (consequently, $\mu_a' < \mu_{m+1}$). On the other hand, if $\mu_a < \mu_{m}$, then $\nu_a'$ will be moved away from $\nu_a$ just enough so that $\nu_a$ is closer to $\nu_m$ than to $\nu_a'$ (consequently, $\mu_a' > \mu_m$). These changes in distribution make the original set of optimal arms, $\{1,\dots,m\}$ no longer optimal under the alternative model $\nu'$. Given that the algorithm returns $\hat{S}_m$, we know that for the event $\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})$ (which is element of the by the stopping time $\tau$ induced $\sigma$-Algebra $\mathcal{F}_{\tau}$), that $\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta$ and $\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta$ (because fixed confidence $\delta$!).

@@

\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

@@

### Matching algorithm strategies

Given these lower bounds, all that is left is to find algorithms which are able to match the complexity. Sadly, not straightforward for Bernoullis.

@@

A very similar application of the KL divergence has been given in Garivier and Kaufmann (2016) to derive a lower bound on the sample complexity in the case of best arm identification. In particular, the transportation Lemma 1 is used again. And a matching algorithm for $K \geq 2$ arms is proposed.

@@

# KL and Bayesian Thresholding Bandits

## Introduction

We have introduced the thresholding bandit problem in chapter 1. The APT algorith described in Locatelli et al. (2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm. However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian. This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean. This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.

In the case of Gaussian distributions with varying variances, for example, it makes sense to take the variance into account; after all, given two Gaussians with equal mean, intuitively we would prefer to get a sample from the distribution of larger variance.

In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians. And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one. However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1. And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters. Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.

Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence. Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits. We expect that results in a similar vain could be derived for thresholding bandits.

To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al. (2017). Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions. Finally, we compare the performance of different algorithms based on simulations and real world data sets.

## Variance Based Algorithms for Thresholding Bandits

Mukherjee et al. (2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB). The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al. (2016). The algorithm itself, however, differs heavily from the APT algorithm. So is AugUCB for example not an anytime algorithm. Furthermore, arms can be deleted in every round if there are "far enough" away from the mean. Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation. While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take the variance into account. From Gabillon et al. (2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$. Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$. $H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.

While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean. Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al. (2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold. If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates. In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event. In order to derive the bound, Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$. Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al. (2016). However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$. Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.

Based on this assumption, the authors show that the probability that an arm has not been eliminated after $m_i$ rounds is given by (compare equation (2) in Mukherjee et al., 2017):

\begin{equation} \label{Mukherjee2017Equation2}
\mathbb{P}(\hat{\mu}_i > \mu_i + 2s_i) \leq \mathbb{P} (\hat{\mu}_i > \mu_i + 2\bar{s}_i) + \mathbb{P}(\hat{v}_i \geq \sigma^2_i + \sqrt{\rho \epsilon_{T_i}})
\end{equation}

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated. The first term is bounded by the Bernstein inequality. In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm. Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012). There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large. To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence. Mukherjee et al. do similarly for their variance based algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)

## New Approaches
